%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Yashjeet}{Luthra}{ \urlstyle{same}\url{https://yashjeet-luthra.branded.me/} \\
\href{mailto:luthra.yashjeet@gmail.com}{luthra.yashjeet@gmail.com} | 8123178018
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Bhilai Institute of Tech}
\descript{B.E in Computer Science}
\location{May 2013 | Durg, C.G \\ Cum. GPA: 7.12}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn://  \href{https://www.linkedin.com/pub/yashjeet-luthra/72/280/3a4}{\custombold{luthraYashjeetLndIn}} \\
Fackbook://  \href{https://www.facebook.com/yashjeetl}{\custombold{luthraYashjeetFbk}} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
.NET MVC 4 \textbullet{} C-sharp \textbullet{} Ruby \textbullet{} Ruby on Rails \textbullet{} Angularjs \textbullet{} Microsoft sql server  \textbullet{} Mysql  \textbullet{}
WCF \textbullet{} jenkins \textbullet{} Msbuild \textbullet{} DbDeploy \textbullet{}  
\sectionsep


\section{Additional Info}
\subsection{Interests}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Playing Cricket \textbullet{} Workout \textbullet{} Cycling \textbullet{} Visiting new place \textbullet{} Reading Noval
\sectionsep


\subsection{Awards and Recognition}
\vspace{\topsep}
\begin{tightemize}
\vspace{\topsep}
\item Rising Star Award in Emids 2015
\item Runner up in Emids cricket league.
\item Core committee member of Ojas Silver Edition.
\item Organizer in Urja 2011.
\item Volunteer in Ojas 2012.
\item Core committee member of Ojas Silver Edition.
\item Participated in Solar Moto G.P in first year.
\item Active member of CSE Cricket.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{ASE }
\descript{| Emids Technologies Pvt Ltd }
\location{From Oct 2013 – Till Date | Bommanahalli, Bangalore}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\textbf{\href{http://www.eMids.com}{Emids}} is an industry leader in the "convergence" of IT and consulting for the healthcare industry, and provides diversified Information Technology (IT) and Business Process Outsourcing (BPO) services. 
\sectionsep

\vspace{\topsep}
\runsubsection{Summary}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Dedicated to result oriented professional
\item Primarily a .NET developer but adapt to other languages.
\item Self-Motivated, energetic and responsible, self-starter and a flexible team member.
\item Believes in honesty commitment and hard work.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\topsep}
\section{Projects}
\runsubsection{SSI Contract Management}
\descript{}
\location{Nov 2013 – Present | Bangalore,KA}
\vspace{\topsep}
SSI is one of the largest clearing houses in the south of USA.CMS was developed for SSI to allow providers to model and manage insurance paper contracts into system as well as effectively handle claims and adjudicate them against modeled contracts in order to compute revenue projections and contractual adjustments for claims. And with this calculated amount user can compare it with actual remit data. User can do adjudication manually as well as system will run background job daily basis to do adjudication for new claims. It also has the ability to forecast contracts. 
\sectionsep

\vspace{\topsep}
\runsubsection{Technology Used}
\location{ .NET MVC 4 | Oop Factory | WCF }
\vspace{\topsep}
\runsubsection{Language Used}
\location{ C-Sharp }
\vspace{\topsep}
\runsubsection{Tool's Used}
\location{ Visual Studio 2013 }
\sectionsep

\runsubsection{Arc 5.0}
\descript{| Emids internal tool}
\location{DEC 2014 – Feb 2015 | Bangalore, KA}
\vspace{\topsep}
ARC 5.0 is an emids internal project that are used to maintain Employee information,project management.
It is an on going project that's need continuous Build and Deployment integration.
\sectionsep

\runsubsection{Tool's Used}
\location{ Jenkins Integration Tools | Web Deploy 3.5 | MsBuild | DbDeploy }

\sectionsep
\runsubsection{Nutritown Order Management}
\descript{| Freelancer Developer }
\location{JAN 2015 – MAY 2015 | Bangalore, KA}
\vspace{\topsep}
Responsible for developing the Order Management System of the company. The system takes in the customers order saves the data into the database.The Middle Tier is built upon ROR and front end is built upon Angular.Js(SPA Application)
\sectionsep

\runsubsection{Tool's Used}
\location{ Ruby | Ruby On Rails | Mysql | Angularjs }

\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}